Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s07_problempinning.tex
Added figures into the problem pinning section

@@

\begin{remark}
    A multi-body-pin qusec is a special case of bar-joint qusecs that we have been studying. As such, the DR planning discussed in Sections \ref{dr} and \ref{recomb} will still go through.
\end{remark}

\begin{proof}
    We can replace each body that has only one pin by a single vertex. A body with 2 pins can be replaced by an edge. A body with 3 pins can be replaced by a triangle. In general, a body with $n$ pins can be replaced by a 2-tree on $n$ vertices. When looking for a DR plan, we treat each body as trivial, so they become the leaves of our plan.
\end{proof}

@@

\begin{definition}
    A body-pin qusec is a multi-body-pin qusec with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin
    \end{itemize}
    Such a body-pin qusec can also be seen as a {\em body-bar qusec} where the bodies are the original bodies and each pin represents 2 bars from one body to another. For such body-bar qusecs, graphs with 1 and 2 dofs can be characterized by being $(3,4)$ and $(3,5)$ tight respectively.
\end{definition}

@@

Body-pin qusecs are of particular interest to us in the context of Example 4 in \ref{intro}. Multi-triangle-pin qusec can be used to reprsent the silica bi-layers described in Example 5 of \ref{intro}, where each triangle is the junction of ``disks''. Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR plan:

@@

\begin{remark}
    All $(k,l)$ tight canonical DR plans are optimal. We can find such a DR plan in the same time complexity as the $(2,3)$ tight case for bar and joint qusecs discussed in Section \ref{dr}.
\end{remark}

>>>>

\begin{figure}\centering
    \includegraphics[width=0.5\linewidth]{img/Silica}
    \caption{Example of 1 layer of a Silica Oxygen glassy structure. This can be thought of as a multi-triangle-pin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins.}
\end{figure}

@@

\begin{remark}
    A multi-body-pin qusec is a special case of bar-joint qusecs that we have been studying. As such, the DR planning discussed in Section \ref{dr} is unchanged and the work in Section \ref{recomb} will still go through with slight modifications.
\end{remark}

\begin{proof}
    We can replace each body that has only one pin by a single vertex. A body with 2 pins can be replaced by an edge. In general, a body with $n$ pins can be replaced by a 2-tree on $n$ vertices. When looking for a DR plan, we treat each body as trivial, so they become the leaves of our plan. The optimal completion problem and approach of Section \ref{dr} are unchanged. The optimal paramaterization problem in Section \ref{dr} now has an additional constraint that all edges in the 2-tree representation of the bodies must be removed together, not individually.
\end{proof}

@@

\begin{definition}
\label{def:body-pin}
    A body-pin qusec is a multi-body-pin qusec with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin
    \end{itemize}
    Such a body-pin qusec can also be seen as a {\em body-bar qusec} where the bodies are the original bodies and each pin represents 2 bars from one body to another. For such body-bar qusecs, graphs with 1 and 2 dofs can be characterized by being $(3,4)$ and $(3,5)$ tight respectively.
\end{definition}

@@

Body-pin qusecs are of particular interest to us in the context of Example 4 in Section \ref{intro}. Multi-triangle-pin qusec can be used to reprsent the silica bi-layers and glassy structures described in Example 5 of Section \ref{intro}, where each triangle is the junction of ``disks'' in the plane. Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR plan:

@@

\begin{remark}
    All $(k,l)$ tight canonical DR plans are optimal. We can find such a DR plan in the same time complexity as the $(2,3)$ tight case for bar and joint qusecs discussed in Section \ref{dr}.
\end{remark}
\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \begin{tikzpicture}[scale=0.8]
        % \tikzstyle{v}=[draw, circle, minimum size=0.1cm, scale=0.7, font=\footnotesize]
        \tikzstyle{v}=[font=\footnotesize]

        \node[v] (a) at (0,0) {A};
        \node[v] (b) at (0,1) {B};
        \node[v] (c) at (1,0) {C};
        \node[v] (d) at (1,1) {D};
        \node[v] (e) at (0,2) {E};
        \node[v] (f) at (1,2) {F};
        \node[v] (g) at (-1,0) {G};
        \node[v] (h) at (-1,1) {H};

        \draw (a) to [bend right=10](b);
        \draw (a) to [bend left=10](b);
        \draw (a) to [bend right=10](c);
        \draw (a) to [bend left=10](c);
        \draw (d) to [bend right=10](c);
        \draw (d) to [bend left=10](c);
        \draw (b) to [bend right=10](d);
        \draw (b) to [bend left=10](d);
        \draw (b) to [bend right=10](e);
        \draw (b) to [bend left=10](e);
        \draw (b) to [bend right=10](h);
        \draw (b) to [bend left=10](h);
        \draw (g) to [bend right=10](h);
        \draw (g) to [bend left=10](h);
        \draw (g) to [bend right=10](a);
        \draw (g) to [bend left=10](a);
        \draw (f) to [bend right=10](e);
        \draw (f) to [bend left=10](e);
        \draw (f) to [bend right=10](d);
        \draw (f) to [bend left=10](d);
    \end{tikzpicture}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}\centering\scriptsize
    \begin{tikzpicture}
    [level 1/.style={sibling distance=8em},
     level 3/.style={sibling distance=1em}, level distance=0.75cm]
        \tikzstyle{n}=[draw, fill, circle]

        \node (a) at (0,0) {A,B,C,D,E,F,G,H}
            child { node {A,B,C,D,E,F} 
                child { node {C,D,E,F}
                    child {node { }}
                    child {node {...}}
                    child {node { }}
                    child {node { }}
                    } 
                child { node (shared) {A,B,C,D}
                    child {node {A}}
                    child {node {B}}
                    child {node {C}}
                    child {node {D}}
                    } 
                }
            child { node {A,B,C,D,G,H} 
                child { node { } }
                child { node {{\bf A,B,G,H}} 
                    child {node { }}
                    child {node {...}}
                    child {node { }}
                    child {node { }}
                }
            };

    \end{tikzpicture}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}

% \begin{subfigure}

% \end{subfigure}
\caption{(a) is an orignal body-pin qusec. (b) is the corresponding body-bar qusec explained in Definition \ref{def:body-pin}. (c) is the 1 dof DR plan for the qusec. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the node in the second level. (d) is the result of adding one such body tot he bold-faced node.}

\end{figure*}
